Microlensing as a possible probe of event-horizon structure in quasars

### 2016-10-03 paper1/ms.tex
changes

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/ch_points.eps}
        \includegraphics[width = 0.48\textwidth]{figures/ch_instances.eps}
\caption{\label{fig:char_points} The characteristic points and instances of a crescent source's one dimensional profile and microlensing lightcurve. }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth]{figures/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained
  from the numerical integration along the ordonata axis of the source
  image is presented in the upper panel. The corresponding
  lightcurve associated to the 1D profile is presented in the lower
  panel. The points $\rm p_2$ and $\rm p_3$ mark the start and 
  end of the equivalent
  dark disk and are associated with the moments of their overlap with
  the caustic: $\rm t_2$ and $\rm t_3$. $\rm h_{w}$ denotes the maximum width of the crescent.}
\end{figure}

>>>>

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/ch_points.eps}
        \includegraphics[width = 0.48\textwidth]{figures/ch_instances.eps}
\caption{\label{fig:char_points} The characteristic points and instances 
of a crescent source's one dimensional profile and microlensing lightcurve.
In the top panel a typical 1D profile  of a crescent source is presented. 
There are two light gray regions that mark the regions of the bright disk 
that are not overlapped by the dark disk. The dark gray band marks the 
region where the two disks overlap. $p_1$ and $p_4$ mark the start and 
end of the bright disk in the 
1D representation. Analogous, $p_2$ and $p_3$ mark the start and 
end of the dark disk.
The bottom panel represents the associated lightcurve with the points 
$t_i$ marking the moment when point $p_i$ overlaps with the caustic.
The gray shades are analogous to the ones in the top panel.
 }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth]{figures/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained
  from the numerical integration along the ordonata axis of a simulated source
  image is presented in the upper panel. The source image was presented in 
 \cite{2012MNRAS.421.1517D} in the top right-most panel of figure 5 
(of the respective paper) as a result of the simulations 
presented in \cite{2009MNRAS.394L.126M}. The corresponding
  lightcurve associated to the 1D profile is presented in the lower
  panel. The points $\rm p_2$ and $\rm p_3$ mark the start and 
  end of the equivalent
  dark disk and are associated with the moments of their overlap with
  the caustic: $\rm t_2$ and $\rm t_3$. $\rm h_{w}$ denotes the maximum width of the crescent.}
\end{figure}
